\cvsection{Projects \& Experience}
\begin{cventries}
  \cventry
    {Cubesatellite Development Intern}
    {NASA Goddard Space Flight Center}
    {Greenbelt, MD}
    {Jun. 2017 -}
    {
      \begin{cvitems}
         \item {Working in the Component Hardware Systems Branch on the hardware development of solid fuel vacuum arc ion thrusters with a variety of applications including formation flying in LEO}
         \item {Responsibilities include development, manufacture, and testing of thruster configurations and accompanying electronics (power supply and plasma arc generation unit). }
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {Michigan Exploration Lab}
    {Ann Arbor, MI}
    {Feb. 2017 -}
    {
      \begin{cvitems}
        \item {Primarily work with the STRATO high-altitude balloon subteam and cubesatellite C\&DH software}
        \item {Completed extensive preparation work for August 2017 launch of still image and video payloads to observe the Great American Eclipse (organized by Montana State University)}
        \item {Improved upon existing data logging and exchange modules for TBEx mission} 
      \end{cvitems}
    }

 
  \cventry
    {Research Assistant | Sponsor: Prof. Anna C. Gilbert, U of Michigan Dept. of Mathematics}
    {Data Collection and Storage Methods on the Arduino}
    {Ann Arbor, MI}
    {Oct. 2016 -}
    {
      \begin{cvitems}
        \item {Implementing an existing sublinearly-efficient sampling algorithm (Gilbert, Strauss, and Tropp) on the Arduino platform for possible use in Internet of Things (IoT) applications}
        \item {Built using the Arduino C-variant and C++ style external libraries}
        \item {Upon completion, the implementation will be tested alongside the existing MATLAB implemention for performance benchmarks}
      \end{cvitems}
    }
    
  \cventry
    {Software Intern}
    {Recon Industrial Controls Corporation}
    {Englewood, NJ}
    {Sep. 2015 - Jun. 2016}
    {
      \begin{cvitems}
        \item {Primarily focused on repackaging LabRecon software in newer versions of the
WINE compatibility environment to work with latest versions of Mac OS}
        \item {Developed software to run on the ESP8266 chip in order serve web pages and
handle serial communication with LabRecon board}
        \item {Utilized a tablet-hosted WiFi network as a means of interfacing with LabRecon
experimenter chip}
      \end{cvitems}
    }
  \cventry
    {Hackathon Organizer}
    {hackBCA Director of Logistics}
    {Hackensack, NJ}
    {Apr. 2015 - Apr. 2016}
    {
      \begin{cvitems}
        \item {Member of Board of Directors for the third iteration of hackBCA, one of the nation's first high school hackathons and first high school hackathon to be included in the MLH hackathon season schedule}
        \item {Managed the expenditure of \$13,000 of resources and food for the hackathon, which drew in over 500 attendees}
        \item { Handled the event schedule, venue arrangements, food distribution, staff
communication, chaperone assignment, and other issues as they arose}
      \end{cvitems}
    }
  \cventry
    {Group Research Project}
    {Locating and Identifying Viable Asteroids (LIVA)}
    {Hackensack, NJ / Hiroshima, Japan}
    {Apr. 2014 - Nov. 2014}
    {
      \begin{cvitems}
        \item {Part of the NASA ICED initiative introduced by Dr. Charlie Camarda}
        \item {Prototyped and built an instrument package with a custom printed circuit board and accompanying
software to detect presence of water in asteroids}
        \item {Collaborated with Kokutai-ji High School in Hiroshima, Japan with support from the
Japanese Ministry of Education}
      \end{cvitems}
    }
  \cventry
    {Camp Organizer}
    {E-Camp Director}
    {Hackensack, NJ}
    {Apr. 2013- Aug. 2015}
    {
      \begin{cvitems}
        \item {Organized and ran E-Camp, an annual week-long program for the 30+ incoming freshman in
the Bergen County Academies's engineering program}
        \item {Along with three other directors, handled the organization of the camp which
included determining the schedule of activities and purchasing \$2800 of supplies in addition to
traditional counselor duties}
      \end{cvitems}
    }
  

\end{cventries}
